Self Regulation Ontology Retest Analyses

### 2018-05-17 code/SRO_Retest_Analyses.Rmd
frisem prep

```{r}
demog_rel_df %>%
  ggplot(aes(icc))+
  geom_histogram(fill = 'grey', alpha = 0.7, color = NA)+
  xlab("ICC")+
  ylab("Count")

ggsave('DemogRelDist.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 5, units = "in", dpi=300)
```

@@

```{r}
t1_2_difference %>%
  ggplot()+
  geom_smooth(aes(as.numeric(days_btw), abs(difference), group=factor(dv)), method='lm', se=FALSE, color = 'grey', alpha = 0.5)+
  geom_smooth(aes(as.numeric(days_btw), abs(difference)), method='lm', color = "black", se=FALSE)+
  theme(legend.title = element_blank())+
  xlab('Days between completion')+
  ylab('Absolute Scaled difference score')

ggsave('DaysBtwEffect.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 300)
```

@@

ggsave('DataCheckOverlappingItems.jpg', p5, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 8, height = 5, units = "in", limitsize = FALSE, dpi = 300)

@@

tmp %>%  
  ggplot(aes(value, fill=sample))+
  geom_density(alpha = 0.5, position='identity', color=NA)+
  # facet_grid(.~stat, scales='free', labeller = label_parsed)+
  scale_fill_manual(breaks=c("boot","lit"),
                       labels=c("Empirical", "Literature"),
                      name="Predictor",
                      values = c("white", "orange"))+
  xlab('Variance Explained')+
  ylab('Density')+
  xlim(0,1)+
  ylim(0,40)

ggsave('LitOnly_Noise_Ceiling.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 300)

tmp %>%  
  ggplot(aes(value, fill=sample))+
  geom_density(alpha = 0.5, position='identity', color=NA)+
  # facet_grid(.~stat, scales='free', labeller = label_parsed)+
  scale_fill_manual(breaks=c("boot","lit"),
                       labels=c("Empirical", "Literature"),
                      name="Predictor",
                      values = c("purple", "orange"))+
  xlab('Variance Explained')+
  ylab('Density')+
  xlim(0,1)+
  ylim(0,40)

ggsave('LitAndBoot_Noise_Ceiling.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 300)
```

>>>>

```{r}
timed_demogs <- c("DoctorVisitsLastMonth","DaysHalfLastMonth","Worthless","DaysPhysicalHealthFeelings","Depressed","EverythingIsEffort","Hopeless","RestlessFidgety","Nervous","DaysLostLastMonth","Last30DaysUsual")

demog_rel_df %>%
  mutate(timed = ifelse(var %in% timed_demogs, 1, 0)) %>%
  ggplot(aes(icc, fill = factor(timed)))+
  geom_histogram(position = "identity", alpha = 0.7, color = NA)+
  xlab("ICC")+
  ylab("Count")+
  scale_fill_manual(values = c("grey", "grey25"))+
  theme(legend.position = "none")

demog_rel_df

ggsave('DemogRelDist.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 5, units = "in", dpi=500)
```

@@

```{r}
t1_2_difference %>%
  ggplot()+
  geom_smooth(aes(as.numeric(days_btw), abs(difference), group=factor(dv)), method='lm', se=FALSE, color = 'grey', alpha = 0.5)+
  geom_smooth(aes(as.numeric(days_btw), abs(difference)), method='lm', color = "black", se=FALSE)+
  theme(legend.title = element_blank())+
  xlab('Days between completion')+
  ylab('Scaled difference score')

ggsave('DaysBtwEffect.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 500)
```

@@

ggsave('DataCheckOverlappingItems.jpg', p5, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 8, height = 5, units = "in", limitsize = FALSE, dpi = 500)

@@

tmp %>%  
  ggplot(aes(value, fill=sample))+
  geom_density(alpha = 0.5, position='identity', color=NA)+
  # facet_grid(.~stat, scales='free', labeller = label_parsed)+
  scale_fill_manual(breaks=c("boot","lit"),
                       labels=c("Empirical", "Literature"),
                      name="Predictor",
                      values = c("white", "orange"))+
  xlab('Variance Explained')+
  ylab('Density')+
  xlim(0,1)+
  ylim(0,40)+
  theme(axis.title.x  = element_text(size=16),
        axis.text.x  = element_text(size=14),
        axis.title.y  = element_text(size=16),
        legend.title  = element_text(size=16),
        legend.text  = element_text(size=16))

ggsave('LitOnly_Noise_Ceiling.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 500)

tmp %>%  
  ggplot(aes(value, fill=sample))+
  geom_density(alpha = 0.5, position='identity', color=NA)+
  # facet_grid(.~stat, scales='free', labeller = label_parsed)+
  scale_fill_manual(breaks=c("boot","lit"),
                       labels=c("Empirical", "Literature"),
                      name="Predictor",
                      values = c("purple", "orange"))+
  xlab('Variance Explained')+
  ylab('Density')+
  xlim(0,1)+
  ylim(0,40)+
  theme(axis.title.x  = element_text(size=16),
        axis.text.x  = element_text(size=14),
        axis.title.y  = element_text(size=16),
        legend.title  = element_text(size=16),
        legend.text  = element_text(size=16))

ggsave('LitAndBoot_Noise_Ceiling.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 500)
```
